Verifying Demonstrations

### 2018-11-28 paper/adversary-model.tex
Points out that the adversary is allowed to submit to S
This is for verifiability.

As to \(S\), \cref{in-system-adversary} corresponds to an adversary who cannot 
even observe the channel between \(P\) and \(S\), \eg when \(P\) uses tools 
such as Tor~\cite{Tor}.
The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
\(S\) learns it; \eg \(S\) is operated outside the adversary's jurisdiction and 
so the adversary cannot control \(S\), but since \(S\) provides public access 
the adversary can (possibly constantly) query it and learn things with little 
delay.
However, it might not be realistic to assume that the channel between \(P\) and 
\(S\) is unobservable for the adversary.
\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
thus perform time-correlation attacks on messages on the network and events 
observed through \(S\).
We capture this in \cref{deanonymizing-storage-adversary}, where \(S\) learns 
the identity of the protester.

>>>>

As to \(S\), \cref{in-system-adversary} corresponds to an adversary who cannot 
even observe the channel between \(P\) and \(S\), \eg when \(P\) uses tools 
such as Tor~\cite{Tor}.
The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
\(S\) learns it; \eg \(S\) is operated outside the adversary's jurisdiction and 
so the adversary cannot control \(S\), but since \(S\) provides public access 
the adversary can (possibly constantly) query it and learn things with little 
delay.
Note that the adversary is also allowed to submit data to \(S\) for storage, 
just like everyone else.

\Cref{deanonymizing-storage-adversary} is a stronger adversary who also can 
observe the channel between \(P\) and \(S\).
\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
thus perform time-correlation attacks on messages on the network and events 
observed from \(S\).
We capture this in \cref{deanonymizing-storage-adversary}, where \(S\) learns 
the identity of \(P\).
